AHABus \& FCORE: A Modular Bus System for High-Altitude Balloon Missions

### 2017-04-24 appendices.tex
Fix wrong datatype in Apx.C

\begin{verbatim}
struct radio_packet {
    00: u8          protocol_version
    01: u8          instrument_id
    04: u16         length
    06: f32         latitude
    08: f32         longitude
    0a: u16         altitude
    0c: b8[length]  data
}
\end{verbatim}

>>>>

\begin{verbatim}
struct radio_packet {
    00: u8          protocol_version
    01: u8          instrument_id
    04: u16         length
    06: i32         latitude
    08: i32         longitude
    0a: u16         altitude
    0c: b8[length]  data
}
\end{verbatim}
